### 2021-07-08 doc/thesis/chapters/dsp.tex
one more

Fig.\ref{fig_channel_baseband_freqs} shows the frequency spectrum of a single channel, located at its carrier- or center frequency.
For a better overview, only the positive spectum part is shown.
The negative part is an exact mirror, because the transmitted and received signals from the antenna are real signals - they do not have an imaginary part.
The spectrum consists of multiple parts. Therefore, it is also referred to as `multiplex signal' in the literature. Several parts are described in the following paragraphs \cite{EbuFmRegulators}\cite{EtsiFmSoundBroadcastingServiceHarmonizedStandard}\cite{ElectronicsNotesFmTutorial}.

\begin{figure}[!h]
  \centering
    \includegraphics[width=9cm]{img/fm-channel-baseband.png}
  \caption{Allocation of frequencies in an FM channel \cite{FigFmChannelFreqSpectrum}.}
  \label{fig_channel_baseband_freqs}
\end{figure}

@@

This chapter describes the demodulation of the information content of an FM broadcast channel, as it is used in commercial FM radio broadcasting.
The assumption here is, that the actual FM demodulation, as described in chapter \ref{sec:algorithms-for-digital-fm-demodulation} is already done correctly.
A frequency spectrum of the multiplex signal of an FM channel is shown in Fig.\ref{fig_channel_baseband_freqs}.

>>>>

Fig.\ref{fig:fm_channel_baseband_freqs} shows the frequency spectrum of a single channel, located at its carrier- or center frequency.
For a better overview, only the positive spectum part is shown.
The negative part is an exact mirror, because the transmitted and received signals from the antenna are real signals - they do not have an imaginary part.
The spectrum consists of multiple parts. Therefore, it is also referred to as `multiplex signal' in the literature. Several parts are described in the following paragraphs \cite{EbuFmRegulators}\cite{EtsiFmSoundBroadcastingServiceHarmonizedStandard}\cite{ElectronicsNotesFmTutorial}.

\includepicture [0.9] [0] {Allocation of frequencies in an FM channel \cite{FigFmChannelFreqSpectrum}.
} {fm_channel_baseband_freqs} {img/draw.io/fm-channel-baseband-freqs}

@@

This chapter describes the demodulation of the information content of an FM broadcast channel, as it is used in commercial FM radio broadcasting.
The assumption here is, that the actual FM demodulation, as described in chapter \ref{sec:algorithms-for-digital-fm-demodulation} is already done correctly.
A frequency spectrum of the multiplex signal of an FM channel is shown in Fig.\ref{fig:fm_channel_baseband_freqs}.
